MultiDataImportPico

### 2023-12-06 Code/MultiDataImportPico.Rmd
read_csv files

Skip <- 19

@@

# This opens a compressed file without decompressing.
TargetData <- read_csv(unz(DataIn, TargetFile),  skip = 20, id = "path", col_names = c("key", "time", "abs-time", "value")) %>% 
  separate(col = path, into = c("path", "Filename"), sep = ":")

>>>>

Skip <- 20

@@

# This opens a compressed file without decompressing.
TargetData <- read_csv(unz(DataIn, TargetFile),  skip = Skip, id = "path", col_names = c("key", "time", "abs-time", "value")) %>% 
  separate(col = path, into = c("path", "Filename"), sep = ":")
